---
title: "DSANRM Tutorial"
author: "Deepak Jaiswal"
date: "04/12/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(BioCro)
```

## Locations
1. Ahmedabad, Gujarat (23.03788, 72.59415) 
2. Allahabad, Uttar Pradesh (23.43605,81.84312)
3. Palakkad, Kerala (10.78564,76.65541)

Website to download the data (https://power.larc.nasa.gov/data-access-viewer/) 

1. User Community: Agroclimatology 
2. Temporal Average: Hourly
3. Enter Lat/Lon: Three locations & corresponding filenames
4. Start Date: 01/01/2001
5. End Date: 12//32/2020
6. Selected Output File Format: CSV
7. Select Parameters:
8. All Sky Surface Photosynthetically Active Radiation
9. Temperature at 2 Meters
10. Relative Humidity at 2 Meters
11. Precipitation
12. Wind Speed at 2 Meters

## Read downloaded weather records and compare three locations
```{r}
ahmedabad <- read.csv("Ahmedabad.csv", skip=13,header = TRUE)
allahabad <- read.csv("Allahabad.csv", skip = 13, header = TRUE)
palakkad <- read.csv("Palakkad.csv",skip = 13, header = TRUE)
```

## Loading modules required for sugarcane simulations
```{r}
source("initial_state.R")
source("ss_modules_list_nowaterstress.R")
source("deriv_modules_list_with_miscanthus_senescence.R")
source("parameters_list_nowaterstress_miscanthus_senescence.R")
```

## Loading (precalibrated/validated) parameters & initial conditions  required for sugarcane simulations
```{r}
source("parameters_list_nowaterstress_miscanthus_senescence.R")
source("initial_state.R")
```

## Defininf output dataframe
1. Planting date: February 1, Harvest date: November 30 
2. No effect of ratooning is included (simulations only for plant crop) 
3. No nutrient (N/P/K) limitations 
4. No irrigation (Water stress is controlled by rainfall) 
```{r}
output_yield = data.frame(ahmedabad = numeric(20), palakkad = numeric(20), allahabad = numeric(20))
```


## Simulations for Ahmedabad
```{r, result=FALSE}
result_index = 1
for (year in 2001:2020){
weather_one_year <- ahmedabad[ahmedabad$YEAR==year,]
num_of_days <- dim(weather_one_year)[1]/24
doy_index = 1
for (i in 1:num_of_days){
weather_one_year$doy[doy_index:(doy_index+23)]=i
doy_index = doy_index+24
}

weather_input_for_BioCro <- data.frame(year = weather_one_year$YEAR, doy = weather_one_year$doy,hour=weather_one_year$HR,
                  solar= (weather_one_year$ALLSKY_SFC_PAR_TOT*4),
                  temp = weather_one_year$T2M,
                  rh = (weather_one_year$RH2M*0.01), windspeed =  weather_one_year$WS2M,
                  precip=weather_one_year$PRECTOTCORR,
                  solardiff=(weather_one_year$ALLSKY_SFC_PAR_TOT*2))

result <- Gro_solver(initial_state =  initial_state,
                     parameters = parameters_list,
                     varying_parameters = weather_input_for_BioCro,
                     steady_state_module_names = ss_modules_list,
                     derivative_module_names = deriv_modules_list, verbose = TRUE)

output_yield$ahmedabad[result_index] = max(result$Stem)
result_index = result_index+1
}

```


## Simulations for Allahabad
```{r, results=FALSE}
result_index = 1
for (year in 2001:2020){
weather_one_year <- allahabad[allahabad$YEAR==year,]
num_of_days <- dim(weather_one_year)[1]/24
doy_index = 1
for (i in 1:num_of_days){
weather_one_year$doy[doy_index:(doy_index+23)]=i
doy_index = doy_index+24
}

weather_input_for_BioCro <- data.frame(year = weather_one_year$YEAR, doy = weather_one_year$doy,hour=weather_one_year$HR,
                  solar= (weather_one_year$ALLSKY_SFC_PAR_TOT*4),
                  temp = weather_one_year$T2M,
                  rh = (weather_one_year$RH2M*0.01), windspeed =  weather_one_year$WS2M,
                  precip=weather_one_year$PRECTOTCORR,
                  solardiff=(weather_one_year$ALLSKY_SFC_PAR_TOT*2))

result <- Gro_solver(initial_state =  initial_state,
                     parameters = parameters_list,
                     varying_parameters = weather_input_for_BioCro,
                     steady_state_module_names = ss_modules_list,
                     derivative_module_names = deriv_modules_list, verbose = TRUE)

output_yield$allahabad[result_index] = max(result$Stem)
result_index = result_index+1
}

```

## Simulations for Palakkad
```{r, results=FALSE}
result_index = 1
for (year in 2001:2020){
weather_one_year <- palakkad[palakkad$YEAR==year,]
num_of_days <- dim(weather_one_year)[1]/24
doy_index = 1
for (i in 1:num_of_days){
weather_one_year$doy[doy_index:(doy_index+23)]=i
doy_index = doy_index+24
}

weather_input_for_BioCro <- data.frame(year = weather_one_year$YEAR, doy = weather_one_year$doy,hour=weather_one_year$HR,
                  solar= (weather_one_year$ALLSKY_SFC_PAR_TOT*4),
                  temp = weather_one_year$T2M,
                  rh = (weather_one_year$RH2M*0.01), windspeed =  weather_one_year$WS2M,
                  precip=weather_one_year$PRECTOTCORR,
                  solardiff=(weather_one_year$ALLSKY_SFC_PAR_TOT*2))

result <- Gro_solver(initial_state =  initial_state,
                     parameters = parameters_list,
                     varying_parameters = weather_input_for_BioCro,
                     steady_state_module_names = ss_modules_list,
                     derivative_module_names = deriv_modules_list, verbose = TRUE)

output_yield$palakkad[result_index] = max(result$Stem)
result_index = result_index+1
}

```


## Plotting results
```{r}
output_yield$year <- seq(2001:2020)
png(file="sugarcane_yield_comparison.png")
lattice::xyplot(palakkad+ahmedabad+allahabad~year, data=output_yield, type = "l", auto.key=TRUE)
dev.off()

write.csv(output_yield, file="sugarcane_yield_comparison.csv")

```



